「赴尘杯」2025 年普通高中学业水平选择性考试适应性演练

### 2025-01-20 Dustbound/English/Dustbound_English_I/paper.tex
feat: :construction: 加入语法填空

\examsetup{
  page = {
    foot-content = 「赴尘杯」英语试题第 ; 页（共 ;页）
  }
}
\backgroundsetup{
  scale=20,
  color=black!10,
  opacity=1,
  angle=45,
  position=current page.center,
  contents={赴尘杯}
}

@@

The answer, it would appear, is fear—blood-thirsty and gruesome aspects of the story, such as the eating of the grandmother by the wolf turned out to be the best preserved of all. \fillin[B]? Tehrani has an idea: ``In an oral context, a story won't survive because of one great teller. \fillin[C].'' Maybe being swallowed whole by a wolf, then cut out of its stomach alive is so gripping that it helps the story remain popular, no matter how badly it's told.

@@

\begin{choices}
\item But his research suggests otherwise
\item Why are these details retained by generations of storytellers, when other features are not
\item It also needs to be interesting when it's told by someone who's not necessarily a great storyteller
\item Folklorists believe that what happens in a story is more central to the story than the characters in it
\item According to folklorists, the impression left by a story’s characters tends to be stronger than that of the events unfolding within it
\item He believes the perennial theme of women as victims in stories like \textit{Little Red Riding Hood} explains why they continue to feel relevant
\item He holds the point that fairy tales continue to be passed down through generations because they frequently depict women as storytellers
\end{choices}

>>>>

\examsetup{
  page = {
    foot-content = 「赴尘杯」英语试题第 ; 页（共 ;页）
  },
  fillin = {
    show-answer = false,
    no-answer-type = counter,
    no-answer-counter-index = 36
  }
}
\backgroundsetup{
  scale=20,
  color=black!10,
  opacity=1,
  angle=45,
  position=current page.center,
  contents={赴尘杯}
}

@@

The answer, it would appear, is fear—blood-thirsty and gruesome aspects of the story, such as the eating of the grandmother by the wolf turned out to be the best preserved of all. \fillin[B]? Tehrani has an idea: ``In an oral context, a story won't survive because of one great teller.\linebreak \fillin[C].'' Maybe being swallowed whole by a wolf, then cut out of its stomach alive is so gripping that it helps the story remain popular, no matter how badly it's told.

@@

\begin{choices}
\item But his research suggests otherwise
\item Why are these details retained by generations of storytellers, when other features are not
\item It also needs to be interesting when it's told by someone who's not necessarily a great storyteller
\item Folklorists believe that what happens in a story is more central to the story than the characters in it
\item According to folklorists, the impression left by a story's characters tends to be stronger than that of the events unfolding within it
\item He believes the perennial theme of women as victims in stories like \textit{Little Red Riding Hood} explains why they continue to feel relevant
\item He holds the point that fairy tales continue to be passed down through generations because they frequently depict women as storytellers
\end{choices}

\begin{flushleft}
  {\bfseries 第三部分 \hspace{0.5em} 语言运用（共两节，满分 30 分）}

  {\bfseries 第一节（共 15 小题；每小题 1 分，满分 15 分）}
\end{flushleft}

阅读下面短文，从每题所给的 A、B、C 和 D 四个选项中选出最佳答案。

\begin{flushleft}
  {\bfseries 第二节（共 10 小题；每小题 1.5 分，满分 15 分）}
\end{flushleft}

阅读下面短文，在空白处填入 1 个适当的单词或括号内单词的正确形式。

As a dog lover, our canine companions always fill me with joy. Whether pedigree or mongrel, tame or stray, whenever I see one, I smile. After all, their loyalty is \fillin[indisputable] (dispute), their companionship is always welcome—they fetch for us, guard for us and even work for us when required. Good old Fido has always been close to \fillin[mine 或 my] (me), and many other's hearts.

Well, not content \fillin[with] just \fillin[warming] (warm) the cockles of your heart, it seems that our four-legged-friends actually lower the risk of cardiovascular disease, according to a 2017 scientific study, which looked at 3.4 million Swedes from 2001 to 2012.

The study concluded that this lower risk, which was particularly evident in owners of hunting breeds, may not just be due to the \fillin[increasing] (increase) physical activity that goes hand-in-hand with owning a dog, but could also be down to dogs increasing the owner's social contact, or \fillin[by] changing the owner's bacterial microbiome, which is the collection of microscopic species that live in \fillin[their] gut. Dogs change the \fillin[dirt] (dirty) in home environments and therefore expose people to bacteria that they would otherwise not encounter.

These effects were particularly marked in those who lived on their lonesome. According to Mwenya Mubanga of Uppsala University and lead author of the study, ``single dog owners had a 33\% reduction in risk of death and an 11\% reduction in risk of cardiac arrest compared to single non-owners.''

However, before your heart skips a beat, Tove Fall, senior author of the study, also adds that there may be limitations. It's possible that the differences between owners and non-owners, which already existed \fillin[before] the dog was bought, could have influenced the results—or that people who are generally more active also tend to get a dog anyway.

It seems that the results are not as clear cut as they initially appear to be, but as far as I'm concerned, that's ok. I love dogs for \fillin[whether] they make me feel and, cardiovascular benefits or not, they'll always be top dog to me—cross my heart.
